%% matter tex
%% starts with section in the maintex

\begin{frame}{Single antenna}
\begin{columns}[onlytextwidth]
\column{0.5\textwidth}
	\begin{itemize}
		\item $320-384$ MHz \hfill P-band
		\item 25m dish
		\item Commensal 
		\item Different baselines possible
		\item Angular resolution $\sim 0.04$
	\end{itemize}

\column{0.5\textwidth}
	\begin{itemize}
		\item vlite-fast codebase developed and maintained by Matthew Kerr
	\end{itemize}
\end{columns}
\end{frame}

\begin{frame}{MPI Coadder \hfill Warp core}
	\begin{itemize}
		\item Incoherent co-addition $\implies$ sensitivity $\sim \sqrt{N_{\rm ant}}$
		\item \emph{One bad apple spoils the bunch} \\
			Median Absolute Deviation (MAD) based time-frequency zapping.
		\item $12$ node GPU-backed Infiniband-connected cluster.
		\item Message Passing Interface tuned for real-time performance.
			\begin{itemize}
				\item \texttt{MCA Collective Reduce = Rabenseifner}
				\item Disable all ethernet (tcp) communications!
				\item \dots
			\end{itemize}
		\item Successfully clocked in days time of operation in one stretch.
	\end{itemize}
\end{frame}

\begin{frame}{Heimdall | GPU program}
	\begin{itemize}
		\item Written by Ben Bardsdell during his PhD at Swinburne!
		\item Matched-filter based approach. 
	\end{itemize}
% 	\begin{verbatim}
% 		for DM in DM-trial
% 			for Width in 2**[0..MaxWidth] 
% 				MatchedFilter (Dedisperse(Input, DM), Width)
% 			end
% 		end
% \end{verbatim}
	\begin{itemize}
		\item DM-level coincidencing \hfill Max S/N
		\item Very high False Positive rates!
	\end{itemize}
\end{frame}

\begin{frame}[allowframebreaks]{Triggering logic | End products}
	\begin{itemize}
		\item Currently applying cuts: 
		\begin{align}
			{\rm S/N} &\geq 8.5 \\
			{\rm DM}  &\geq 50 {\rm pc/cc} \\
			{\rm Width} &\leq 100 {\rm ms}
		\end{align}
		\item Two mutually exclusive trigger channels: 
			\begin{itemize}
				\item Filterbank triggering. \hfill \emph{above cuts}
				\item Voltage triggering. \hfill S/N $\geq 25$
			\end{itemize}
		\item End products
			\begin{description}
				\item[Filterbank Triggering] \\ 
					Binary JSON file. \\
					Filterbank data.
				\item[Voltage Triggering] \\
					Raw binary file dump. \\
					Two polarization voltage series.
			\end{description}
		\item An $8$-second of voltage data needs $\sim 48$x more space than filterbank data. 
		\item Low frequency $\implies$ DM-delay is already large!
	\end{itemize}
\end{frame}

\begin{frame}{Codebases}
\begin{columns}[onlytextwidth]
	\column{0.5\textwidth}
	\begin{itemize}
		\item \textbf{\large Asgard} \hfill C++11
		\item MPI Coadder
		\item Filterbank triggering
		\item Regular data analysis, visualization, and meta analysis.
		\item C++ $\sim 7k$ loc
		\item Python $\sim 2k$ loc
	\end{itemize}

	\column{0.5\textwidth}
	\begin{itemize}
		\item \textbf{\large vlite-fast} \hfill C,CUDA
		\item Maintained and developed by \textbf{ Matthew Kerr } \emph{ (co-advisor) }
		\item Voltage packets from antennas $\to$ filterbanking on GPU
	\end{itemize}
\end{columns}
\end{frame}